\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,shapes.geometric}

\title{IndiciumForge: A Contract-First Open Core for Evidence-First Financial Research Workflows}
\author{Zhengze Yu\thanks{\texttt{cavarad0ssi@outlook.com}}}
\date{July 2026}

\newcommand{\schema}[1]{\texttt{#1}}
\newcommand{\pkg}[1]{\texttt{#1}}
\newcommand{\claim}[1]{\textsuperscript{\textsf{#1}}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\begin{document}
\maketitle

\begin{abstract}
Financial research pipelines frequently combine data ingestion, proprietary signals,
operator-local state, and implicit execution assumptions in ways that obscure what was
knowable at each staged decision. Migrating away from legacy systems compounds the problem
when teams copy modules instead of preserving observable behavior against frozen references.

IndiciumForge is an open-core Python architecture whose primary outputs are versioned
research artifacts--JSON stage states, CSV review tables, and chain summaries--rather
than orders or portfolio actions. Stable contracts and YAML pack loaders let operator-local
extensions attach without forking core semantics. A manifest audit CLI validates structural
completeness; golden and parity comparators evaluate semantic agreement against exported
reference trees without importing legacy runtime code.

We describe seven contributions: contract-first packaging, artifact schema audit,
recipe/session orchestration, an explicit open-core boundary, golden parity methodology,
agent-friendly governance, and real quant capability behind four audited ports--factor analytics (cross-sectional IC and Fama-MacBeth slopes), portfolio optimization (mean-variance Markowitz), a vectorized backtester, and analytic option pricing (Black-Scholes)--demonstrated end-to-end on a synthetic A-share golden panel and, through a global (US-equity) OpenBB adapter, an offline-by-default public demo. A three-layer
validation story combines public golden tests,
a synthetic parity demo, and category-level operator sign-off without disclosing private
rows or paths. IndiciumForge is a quantitative finance framework: it is not a trading system, not
investment advice, and not a broker execution platform.
\end{abstract}

\noindent\textbf{Keywords:} research workflows; software architecture; artifact audit;
open core; reproducibility; financial research systems.

\section{Introduction}

Quantitative and fundamental research groups need workflows that support two audit
questions at every stage: what evidence existed at the time, and whether an independent
reviewer can verify that evidence without rerunning hidden state. Execution-optimized stacks
prioritize latency and fill quality; notebook-centric workflows lack schema discipline and
make regressions expensive to detect.

IndiciumForge targets the middle ground: evidence-first financial research implemented as
auditable artifacts behind explicit contracts. The open-source repository ships ports,
schemas, synthetic fixtures, a reference CLI, manifest audit, golden tests, and a parity
harness. Proprietary data adapters, factor detectors, and production recipe bodies remain
in operator-local packs.

\paragraph{Contributions.}
This paper makes seven software-architecture contributions:
\begin{enumerate}[leftmargin=*]
  \item Contract-first open core: workflow stages consume port interfaces and pack loaders, not vendor SDKs.\claim{C13-C15}
  \item Artifact schemas and audit CLI: \schema{indiciumforge.*} schema IDs plus structural validation.\claim{C03-C04}
  \item Recipe and session workflow model: cyclic session contracts with domain-specific recipes.\claim{C16-C18}
  \item Open-core/private-extension boundary: an ADR-governed IP and security split.\claim{C12,C29}
  \item Golden artifact and parity methodology: exported references and five parity dimensions.\claim{C05-C11}
  \item Agent-friendly governance: ADRs, agent rules, and in-repository skills for safe automation.\claim{C32-C33}
  \item Real quant capability: four ports--analytics, portfolio, backtest, pricing--with reference adapters (an A-share golden snapshot and an opt-in global OpenBB US-equity adapter), a deterministic end-to-end pipeline behind \texttt{indiciumforge quant}, and an offline-by-default public demo (\texttt{quant openbb-demo}).\claim{C43-C53, ADR-0026, ADR-0027}
\end{enumerate}

\paragraph{Non-claims.}
IndiciumForge does not execute live trades or broker orders, provide investment advice,
ship proprietary alpha detectors in the public repository, or claim full replacement of
every legacy workflow surface. Parity \texttt{all\_match} on an operator golden date is
research audit evidence, not production certification.

\section{Problem Statement}

Production research stacks often merge raw and derived data paths, proprietary signal
definitions, local calibration state, and assumptions about session timing or execution
feasibility. When these concerns share one codebase without artifact contracts, reviewers
cannot reconstruct point-in-time evidence. Regression testing devolves into manual diffing
of opaque outputs.

Migration from legacy implementations creates a failure mode of its own: copying modules imports
hidden path assumptions and domain rules that should not become universal core semantics.
IndiciumForge preserves observable behavior against the frozen reference label
\schema{indiciumgrid-golden-v1} under eleven anti-inheritance rules (Appendix~A), recording
behavior outside the covered surface as an intentional change or unsupported gap.\claim{C08,C10,C11,C29,C30}

\section{System Architecture}

IndiciumForge v2.0.0 ships three installable packages:
\begin{center}
\begin{tabular}{ll}
\toprule
Package & Responsibility \\
\midrule
\pkg{indiciumforge-core} & Domain models, ports, artifact I/O, manifest audit, parity models \\
\pkg{indiciumforge-workflow} & Market gate kernel, daily review skeleton, workflow chain runner \\
\pkg{indiciumforge-cli} & Typer CLI exposing workflow, artifact, factor, provider, parity, and quant commands \\
\bottomrule
\end{tabular}
\end{center}

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  boundary/.style={draw, dashed, rounded corners, align=center, inner sep=7pt,
                   text width=3.55cm, minimum height=2.45cm},
  refbox/.style={draw, dashed, rounded corners, align=center, inner sep=7pt,
                 text width=3.55cm, minimum height=1.25cm},
  arrow/.style={-{Latex[length=2mm]}, thick}
]
\node[boundary] (open) {\textbf{Open Core}\\[0.2cm]
  core ports and schemas\\
  workflow runners\\
  CLI commands};
\node[boundary, right=1.25cm of open] (priv) {\textbf{Operator-local Extensions}\\[0.2cm]
  data provider packs\\
  factor detector packs\\
  recipe extension packs};
\node[refbox, below=1.0cm of priv] (ref) {\textbf{Read-only Legacy Reference}\\[0.15cm]
  frozen artifact store};

\draw[arrow] (open.east) -- (priv.west);
\draw[arrow] (open.south east) -- (ref.west);
\end{tikzpicture}
\caption{System boundary. The open core exposes ports and contracts. Operator-local
extensions supply data, factors, and recipe logic. Frozen legacy references support parity
comparison only; they are not imported at runtime.}
\label{fig:boundary}
\end{figure}

\paragraph{Quant analytics, optimization, backtest and pricing.}
\pkg{indiciumforge\_core.quant} mirrors the \pkg{factors} packaging pattern: each submodule
(\texttt{analytics}, \texttt{portfolio}, \texttt{backtest}, \texttt{pricing}) declares a
\verb|typing.Protocol| port, frozen request/result dataclasses, a concrete adapter, a
registry, and a pack loader.\claim{C43} Adapters lazily import heavy dependencies behind
\verb|_require_*| helpers so the package imports with only the core install; optional deps
sit behind the \texttt{[analytics]} (statsmodels, scipy), \texttt{[portfolio]} (cvxpy), and
\texttt{[data]} (akshare, lxml) and \texttt{[openbb]} (OpenBB, US-equity) extras.\claim{C44-C47, ADR-0026, ADR-0027} The end-to-end pipeline
\verb|run_quant_pipeline| and the \texttt{indiciumforge quant} CLI group compose these
ports.\claim{C49,C50}

\section{Contract-First Design}

Workflow code depends on protocols rather than concrete data vendors. The session-aware
data provider port, factor detector port, and recipe extension port follow the same pack
loading pattern. YAML packs declare \schema{indiciumforge.<type>.v1} schemas and reference
entry-point modules or nested configuration files. Public fixtures demonstrate the mechanism;
operators keep live data adapters and proprietary detectors in private repositories.

Breaking namespace changes bump the major release version. The v2.0.0 rebrand from the
legacy \schema{lucerna.*} namespace includes a one-release compatibility shim that accepts
deprecated IDs with warnings.

\paragraph{Design rationale.}
IndiciumForge does not try to replace a general task scheduler, data lake, or backtesting
engine. Its reusable minimum is narrower: namespaced stage schemas, explicit extension
ports, manifest audit, and parity verdicts for exported reference artifacts. This combination
lets a team keep proprietary adapters and detectors outside the public repository while still
reviewing whether an observable research workflow preserved behavior. In contrast, a generic
DAG can schedule the same stages but does not by itself define the financial-research artifact
contracts or the accepted verdict taxonomy.

\section{Artifact Schema and Manifest Audit}

Each machine-readable artifact carries a \texttt{schema} field using the
\schema{indiciumforge.*} namespace. Stage bundles are stored under predictable directories
such as \texttt{workflows/\{YYYYMMDD\}/<stage>/}. The manifest auditor checks required files,
JSON parseability, expected schema IDs, and trade-date consistency.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  node distance=1.1cm and 1.2cm,
  box/.style={draw, rounded corners, align=center, minimum width=2.5cm, minimum height=0.8cm},
  arrow/.style={-{Latex[length=2mm]}, thick}
]
\node[box] (input) {fixture or\\provider};
\node[box, right=of input] (recipe) {recipe\\runner};
\node[box, right=of recipe] (artifacts) {artifact\\store};
\node[box, above right=0.7cm and 1.0cm of artifacts] (audit) {manifest\\audit};
\node[box, below right=0.7cm and 1.0cm of artifacts] (parity) {golden/parity\\compare};
\node[box, right=of parity] (verdict) {verdict\\report};
\node[box, below=0.8cm of artifacts] (ref) {reference\\artifacts};
\draw[arrow] (input) -- (recipe);
\draw[arrow] (recipe) -- (artifacts);
\draw[arrow] (artifacts) -- (audit);
\draw[arrow] (artifacts) -- (parity);
\draw[arrow] (ref) -- (parity);
\draw[arrow] (parity) -- (verdict);
\end{tikzpicture}
\caption{Runtime data flow. Research inputs flow through recipe runners into versioned
artifacts. Manifest audit validates structure; golden and parity comparators evaluate
semantics against reference trees.}
\label{fig:runtime}
\end{figure}

Structural audit is separate from semantic golden comparison. For example, manifest audit can
detect a missing market gate summary before the semantic comparator evaluates strict candidate
sets.

\section{Recipe and Session Model}

IndiciumForge generalizes operator-linear folders into session-cyclic checkpoints linked by
typed handoff artifacts. Core types include asset domains, session models, workflow recipes,
checkpoints, evidence stage references, and handoff artifacts.

The default A-share daily research recipe composes awareness, post-close discovery, preopen
handoff, optional factor scan, and market gate stages. Names such as \texttt{post\_close} are
recipe compatibility labels rather than universal lifecycle enums. Other domains can define
alternate recipes under the same session contracts.

\section{Open-Core / Private-Extension Boundary}

\begin{center}
\begin{tabular}{ll}
\toprule
Open-source repository & Operator-local private packs \\
\midrule
Ports, schemas, loaders & Live data adapters \\
Synthetic fixtures and demo detectors & Proprietary factor logic \\
Recipe runner and extension loader & Production recipe stage implementations \\
Parity harness and synthetic reference demo & Legacy output mirrors, credentials, reference trees \\
\bottomrule
\end{tabular}
\end{center}

This boundary keeps credentials, account identifiers, calibrated policies, and proprietary signal
logic out of the public repository while still enabling real deployments.

\section{Golden Artifact and Parity Methodology}

The public golden layer pins a frozen reference and lists five market-gate scenarios. Public
tests assert semantic agreement with exported expected artifacts. A synthetic parity demo
exercises the same harness without private paths.

\begin{table}[t]
\centering
\small
\begin{tabularx}{\linewidth}{lYl}
\toprule
Evidence layer & Public or reported evidence & Claim IDs \\
\midrule
Package surface & Three installable packages and the \texttt{indiciumforge} CLI & C01, C02 \\
Static and unit gates & Ruff in CI; pytest reported 250 passed and 1 skipped at draft time & C19, C20 \\
Golden market gate & Five exported market-gate scenarios under \schema{indiciumgrid-golden-v1} & C05, C10 \\
Synthetic parity & Public \texttt{parity\_reference\_demo} exercises the harness without private paths & C09, C22 \\
Quant pipeline & Deterministic factor$\to$analytics$\to$optimize$\to$backtest on the synthetic golden panel & C43-C51, ADR-0026 \\
Public demo & Offline \texttt{quant openbb-demo} on a committed synthetic US-equity sample; opt-in OpenBB adapter & C52, C53, ADR-0027 \\
Governance & 26 ADRs plus anti-inheritance rules and agent onboarding documents & C29, C32, C33 \\
\bottomrule
\end{tabularx}
\caption{Artifact-based evidence used in this paper. The table reports software and
audit evidence only; it does not report trading performance, investment recommendations, or
broker execution results.}
\label{tab:evidence}
\end{table}

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  node distance=0.8cm and 0.8cm,
  box/.style={draw, rounded corners, align=center, minimum width=2.2cm, minimum height=0.72cm},
  small/.style={draw, rounded corners, align=center, minimum width=2.25cm, minimum height=0.62cm},
  arrow/.style={-{Latex[length=2mm]}, thick}
]
\node[box] (config) {parity\\config};
\node[box, right=of config] (runner) {workflow\\chain};
\node[box, right=of runner] (actual) {actual\\artifacts};
\node[box, below=of actual] (ref) {reference\\root};
\node[box, right=of actual] (cmp) {candidate\\comparator};
\node[small, right=0.75cm of cmp] (d3) {preopen\\handoff};
\node[small, above=0.23cm of d3] (d2) {post-close\\handoff};
\node[small, above=0.23cm of d2] (d1) {daily\\review};
\node[small, below=0.23cm of d3] (d4) {market-gate\\strict};
\node[small, below=0.23cm of d4] (d5) {chain\\summary};
\node[box, right=0.85cm of d3] (report) {parity\\run report};
\draw[arrow] (config) -- (runner);
\draw[arrow] (runner) -- (actual);
\draw[arrow] (actual) -- (cmp);
\draw[arrow] (ref) -- (cmp);
\draw[arrow] (cmp) -- (d1);
\draw[arrow] (cmp) -- (d2);
\draw[arrow] (cmp) -- (d3);
\draw[arrow] (cmp) -- (d4);
\draw[arrow] (cmp) -- (d5);
\draw[arrow] (d1) -- (report);
\draw[arrow] (d2) -- (report);
\draw[arrow] (d3) -- (report);
\draw[arrow] (d4) -- (report);
\draw[arrow] (d5) -- (report);
\end{tikzpicture}
\caption{Artifact parity flow. The harness runs a recipe chain into an artifact root, compares
five configured dimensions against a reference root, and emits a parity report with
per-dimension verdicts.}
\label{fig:parity}
\end{figure}

The parity harness evaluates daily review structure, post-close handoff shape, preopen
handoff shape, market-gate strict semantics, and workflow chain summary fields. Reports carry
a research-audit disclaimer. Historical \schema{indiciumgrid.*} IDs remain only in frozen
golden expected artifacts.

\section{Case Study: A-Share Factor-to-Backtest Pipeline}
\label{sec:case-ashare}

\paragraph{9.1 Data.}
This release instantiates the four quant ports with reference adapters and wires them into an
end-to-end pipeline \verb|run_quant_pipeline|.\claim{C43-C50} To keep the demonstration
reproducible and honest, the pipeline runs on a committed synthetic A-share-like panel
(\texttt{tests/fixtures/golden\_ashare/panel.parquet}, 36 assets $\times$ 521 trading
dates) served by \texttt{GoldenSnapshotProvider}.\claim{C48} The panel is generated by a
fixed-seed script with a persistent AR(1) trend, so the factor carries positive and
horizon-increasing IC--a credible demo signal, not a fabricated one. All numbers below are
byte-deterministic across runs and locked by \texttt{tests/golden/test\_quant\_pipeline.py}.
\claim{C49}

\paragraph{9.2 Factor.}
A trailing-\texttt{lookback} momentum factor is evaluated over forward horizons
$h \in \{1,5,10\}$. IC is the cross-sectional Spearman rank correlation of factor versus
forward return; the Fama-MacBeth slope is the per-date cross-sectional OLS slope aggregated
over time with a t-statistic.

\paragraph{9.3 Evaluation (IC / Fama-MacBeth).}
\begin{table}[t]
\centering
\small
\begin{tabularx}{\linewidth}{lYYYYl}
\toprule
Horizon $h$ & IC mean & IC std & IR & Positive \% & t-stat \\
\midrule
1 & 0.0347 & 0.1651 & 0.21 & 58.3 & 4.71 \\
5 & 0.4056 & 0.1418 & 2.86 & 99.8 & 64.03 \\
10 & 0.6369 & 0.1004 & 6.34 & 100.0 & 141.97 \\
\bottomrule
\end{tabularx}
\caption{Factor analytics on the synthetic golden panel (n = 501 dates per horizon).
Fama-MacBeth slope mean 0.00786, t-stat 5.18 (n = 502); rank-weight turnover 0.134. IC
rises with horizon because the synthetic trend is persistent--the opposite of the usual
IC-decay pattern, reported exactly as the engine produces it.}
\label{tab:quant-analytics}
\end{table}

\paragraph{9.4 Optimization (Markowitz).}
At the final rebalance, mean-variance optimization yields expected return 0.00278, expected
risk 0.00861, Sharpe 0.322 (long-only, weight bounds).

\paragraph{9.5 Backtest.}
The vectorized backtest
(prior-period weights, flat cost, no look-ahead) with \texttt{rebalance\_every = 10} and
\texttt{cost\_bps = 5} reports total return 0.4102, annualized return 0.1809, annualized
volatility 0.1254, Sharpe 1.44, max drawdown $-0.0987$, Calmar 1.83 (n = 521); portfolio
weights sum to 1.0.

\paragraph{9.6 Reproduction.}
The end-to-end pipeline reproduces from a clean checkout via
\verb|indiciumforge quant pipeline --panel tests/fixtures/golden_ashare/panel.parquet --rebalance-every 10|
(Section~\ref{sec:repro}); all reported numbers are byte-locked by
\texttt{tests/golden/test\_quant\_pipeline.py}.\claim{C49,C50}

\paragraph{9.7 Global public demo (OpenBB).}
The same pipeline runs on a global (US-equity) universe through a second reference adapter,
\texttt{OpenBBDataProvider}, which fetches daily OHLCV via the OpenBB
Platform behind an opt-in \texttt{[openbb]} extra (routing to the token-free yfinance
vendor).\claim{C52, ADR-0027} To keep a fresh clone or PyPI install runnable with no network
and no API keys, \texttt{indiciumforge quant openbb-demo} is \emph{offline by default}: it
reads a committed synthetic sample panel shipped as package data (eight US tickers, 129
dates, 1{,}032 rows) whose manifest flags \texttt{not\_real\_market\_data:\ true}, and writes
an auditable \texttt{summary.json} (IC-by-horizon, optimization, backtest) plus the panel
manifest.\claim{C53} A \texttt{-{}-online} flag opts into a real fetch. A contract test with a
faked OpenBB result object exercises the adapter's coercion, normalization, and error paths
without touching the network, so default CI stays deterministic (ADR-0027).

\paragraph*{Scope of these numbers.}
They are computed on the synthetic golden panel (and, for the public demo, a synthetic
US-equity sample) and demonstrate \emph{framework correctness
and pipeline wiring}, not market performance, not a live-trading backtest, and not
investment advice. The vectorized backtester is daily, single-asset-return, and cost-flat
only; it models no slippage, market impact, or intraday dynamics (Section~``Limitations'',
ADR-0026). The forbidden trading-performance claim remains in force for any real-market
assertion.

\section{Availability and Governance}

IndiciumForge ships agent-facing guidance alongside human documentation: AGENTS.md,
architecture decision records, onboarding maps, and in-repository skills for orientation,
extension authoring, and release audit. These documents encode what automation must not do:
inherit legacy paths, publish private data, or treat research artifacts as execution signals.
The source repository is publicly available under the Apache-2.0 license. Packages are
published on PyPI at v2.0.1, while MCP and plugin surfaces remain documented as future operational work.

\section{Reproducibility}
\label{sec:repro}

From a clean checkout of tag \texttt{v2.0.1}:
\begin{verbatim}
pip install -e packages/indiciumforge-core \
            -e packages/indiciumforge-workflow \
            -e packages/indiciumforge-cli \
            -e ".[dev]"
python -m ruff check .
python -m pytest -q
indiciumforge parity run \
  --parity-config tests/fixtures/parity_reference_demo/parity_config_demo.yaml \
  --artifact-root /tmp/indiciumforge-parity-demo
\end{verbatim}
At draft time the public suite reported 250 passing tests and one skipped test. The parity
command emits a \texttt{parity\_run\_report.json} with dimension-level verdicts.

The \texttt{quant} command group runs without the optional \texttt{[analytics]}/\texttt{[portfolio]}
extras because its commands import heavy deps lazily:
\begin{verbatim}
indiciumforge quant pipeline \
  --panel tests/fixtures/golden_ashare/panel.parquet --rebalance-every 10
indiciumforge quant price \
  --spot 100 --strike 100 --maturity 1 --rate 0.05 --volatility 0.2 --type call
# Global public demo (offline by default; no network, no API keys):
indiciumforge quant openbb-demo --artifact-root /tmp/openbb_demo
\end{verbatim}
All reported numbers are byte-locked by \texttt{tests/golden/test\_quant\_pipeline.py} on the
synthetic golden panel; the OpenBB demo's offline sample is deterministic package data.\claim{C49,C50,C53}

\section{Limitations and Threats to Validity}

IndiciumForge is not a trading system, investment adviser, or broker execution platform. Public
workflows use synthetic fixtures by default. Manifest audit proves structural completeness, not
economic correctness. The public repository does not include proprietary detectors, private
reference trees, account artifacts, or live provider credentials. Operator-local L3 evidence is
self-reported at category level; it is useful for migration sign-off but is not a third-party
replication. Accounting-risk anomaly detection is future work only.

The quant engine is scoped deliberately: the vectorized backtester is daily,
single-asset-return, and cost-flat only, modeling no slippage, market impact, or intraday
dynamics; pricing is analytic European Black-Scholes only; the A-share demonstration uses a
\emph{synthetic} golden panel, so all reported metrics demonstrate framework correctness
rather than market or live-trading performance.\claim{C43-C51, ADR-0026} QuantLib, rqalpha,
and qlib integration are out of scope for this release; the ports remain swappable for alternative
adapters.

\section{Related Work}

IndiciumForge sits between several families of tools. Workflow systems such as Apache Airflow
\cite{airflowdocs} and Snakemake \cite{koster2012snakemake} provide scheduling and dependency
management. Experiment and data tools such as MLflow \cite{mlflow2018}, DVC
\cite{dvcdocs}, and Great Expectations \cite{greatexpectationsdocs} help track runs, data
versions, or data quality. Trading and research stacks such as Zipline \cite{ziplinedocs},
Backtrader \cite{backtraderdocs}, and Qlib \cite{qlib2020} focus on backtesting, strategy
research, or quantitative investment workflows. Provenance standards such as W3C PROV
\cite{provdm} provide a broader model for representing entities, activities, and agents.
Software-engineering work on legacy code and technical debt motivates IndiciumForge's
emphasis on characterization evidence and explicit system boundaries \cite{feathers2004legacy,sculley2015hidden}.

\begin{table}[t]
\centering
\small
\begin{tabularx}{\linewidth}{lYYY}
\toprule
Family & Primary output & Typical strength & IndiciumForge contrast \\
\midrule
Workflow schedulers & Task runs and DAG state & Scheduling and retries & Stage artifacts and parity verdicts are first-class \\
Data/experiment tools & Versioned data, metrics, expectations & Dataset and run management & Multi-file financial-research bundles and manifest audit \\
Backtest/trading frameworks & Returns, orders, positions, simulations & Strategy evaluation & Broker execution and advice are out of scope \\
Provenance standards & General provenance graphs & Interoperable provenance model & Lightweight local audit via schema IDs and stage states \\
\bottomrule
\end{tabularx}
\caption{Positioning against adjacent tool families. IndiciumForge is not a general
scheduler, data-versioning system, or backtesting engine; its contribution is the combination
of financial-research artifact contracts, open-core extension boundaries, and parity evidence.}
\label{tab:related}
\end{table}

Its evaluation is artifact-based: tests, golden scenarios, parity reports, ADRs, and
boundary-preserving migration evidence. This differs from benchmark-oriented toolbox papers:
IndiciumForge does not claim model accuracy, trading performance, or benchmark-style
leaderboard results.

\section{AI Assistance Disclosure}

Drafting and repository-maintenance workflows used AI coding assistants, including Cursor and
Codex, to generate draft text, LaTeX conversions, diagrams, and audit prompts. Human review
retained responsibility for claim selection, private-boundary enforcement, citation curation,
and final submission decisions. The claims register is used as a guard against unsupported
technical statements.

\section{Future Work}

Future work includes point-in-time accounting-risk anomaly detection, research dossier
contracts, MCP tools for manifest and parity inspection, IDE plugin packaging of agent skills,
and additional domain recipes. These directions should retain the research-audit boundary and
avoid embedding competition- or broker-specific execution paths into the open core.

\section{Conclusion}

IndiciumForge shows that financial research workflows can be restructured around auditable
artifacts and explicit contracts, enabling legacy migration evidence through golden and parity
methodology rather than module inheritance. The architecture prioritizes reviewer trust and
reproducible stage evidence over execution latency, making it appropriate for research audit
rather than broker routing.


\appendix
\section{Migration Evidence and Anti-Inheritance Rules}
\label{app:migration}

IndiciumForge preserves observable behavior against the frozen reference label
\schema{indiciumgrid-golden-v1} under eleven anti-inheritance rules; behavior outside the
covered surface is recorded as an intentional change or unsupported gap. The rules guard the
public core against hidden legacy paths, network fetches, and direct promotion of raw provider
output into strict gate decisions.

\paragraph{Three-layer migration evidence.}

The validation story is intentionally layered. Layer L1 uses public golden market-gate tests,
including strict-pass evidence. Layer L2 uses a synthetic parity demo. Layer L3 is an
operator-local sign-off summarized only at category level. No private paths, tickers, row-level
data, or trading performance appear in this section.

\begin{table}[t]
\centering
\small
\begin{tabularx}{\linewidth}{lY}
\toprule
Layer & Evidence summary \\
\midrule
L1: OSS golden & Five public market-gate scenarios exercise strict, observation, watch, and rejected bucket semantics. The public golden layer includes strict-pass evidence. \\
L2: synthetic parity & The public parity demo exercises the harness path and includes strict-count evidence without private paths. \\
L3: operator sign-off & On golden date \texttt{2026-07-03}, five of five parity dimensions matched and the aggregate verdict was \texttt{all\_match: true}. No mismatch was attributed to an IndiciumForge open-core bug or private extension defect. \\
\bottomrule
\end{tabularx}
\caption{Three-layer migration evidence. L1 and L2 are public and reproducible; L3 is
reported only as category-level sign-off to preserve the private-extension boundary.}
\label{tab:case-layers}
\end{table}

The L3 golden date covered the dimensions shown in Table~\ref{tab:l3-dimensions}. Two other
candidate dates were intentionally classified as unsupported gaps rather than failures: the
\texttt{2026-06-24} frozen reference layout lacked the stage directory needed for parity
prepare, and the \texttt{2026-06-23} legacy post-close layout lacked the required handoff
artifact. These blocked dates document reference coverage limits, not open-core defects.

\begin{table}[t]
\centering
\small
\begin{tabularx}{\linewidth}{lY}
\toprule
Parity dimension & Golden-date category verdict \\
\midrule
\texttt{daily\_review\_structure} & match \\
\texttt{post\_close\_handoff\_shape} & match \\
\texttt{preopen\_handoff\_shape} & match \\
\texttt{market\_gate\_strict\_semantics} & match \\
\texttt{workflow\_chain\_summary\_v4} & match \\
\bottomrule
\end{tabularx}
\caption{Category-level L3 verdicts for golden date \texttt{2026-07-03}. The table mirrors
the reconciled v1.0-rc1 evidence summary without disclosing private artifacts.}
\label{tab:l3-dimensions}
\end{table}

The frozen operator reference contains no \texttt{strict\_count > 0} date. Strict-pass
semantics are therefore supported by L1 public golden scenarios and L2 synthetic parity rather
than by the private frozen-reference export. This distinction prevents the case study from
over-claiming production coverage while preserving the useful behavioral migration evidence.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
